\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[russian]{babel}

\moderncvstyle{classic}
\moderncvcolor{green}

\usepackage[utf8]{inputenc}
\usepackage[colorlinks=true, urlcolor=blue, unicode]{hyperref}
\usepackage[scale=0.75]{geometry}

\name{Solozhenkin}{Sevastyan Alekseevich}

\phone[mobile]{+7(903)729-59-70}
\email{sevsol2512@gmail.com}
\date{}

\begin{document}

\opening{Dear mobile CPU team, }
\closing{Sincerely, }

\makelettertitle
\hspace{0.5cm}
My name is Sevastyan Solozhenkin. I am currently a first-year student at Phystech School of Radio Engineering and Computer Technology MIPT, in specialization ”Informatics and
Computation Technology”.

\hspace{0.5cm}
In school, I was unsure about my future career path. However, I enjoyed studying physics, mathematics, and programming. I took various programming courses, ranging from Sirius courses to Yandex Lyceum. When it came time to choose a university, I faced a difficult decision. I had won numerous Olympiads in physics and mathematics, which opened doors to many universities and programs. I chose MIPT because of its strong community and numerous opportunities. I opted for FRKT because it allows me to explore mathematics, physics, and programming equally. I wanted to take my time to decide which field to dedicate my life to.

\hspace{0.5cm}
During the summer programming school led by Ilya Rudolfovich Dedinsky, I realized that
programming was my true passion. Dedinsky’s course combines interesting large projects that seamlessly transition into one another. I devoted almost all my time to programming.

\hspace{0.5cm}
Now, I need to choose a specific area within IT to focus on. This decision is as challenging as the one I faced after graduating from school.

\hspace{0.5cm}
I enjoyed optimizing programs and analyzing compiler-generated code \href{https://github.com/sevaphasol/mandelbrot}{in an assignment
from I.R. Dedinsky’s course}. Among the proposed directions, the mobile CPU group under the supervision of Sergey Lisitsyn interested me the most. I read \href{https://cyberleninka.ru/article/n/sbor-profilnoy-informatsii-s-pomoschyu-trass-ispolneniya-prilozheniya-dlya-staticheskoy-optimiziruyuschey-binarnoy-translyatsii/viewer}{an article} about optimizing
executable code by rearranging ”hot” and ”cold” functions. I believe I would enjoy working in this area. Therefore, I would be delighted to participate in a summer internship to gain experience.

\makeletterclosing

\end{document}
